Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 robdml.tex
tex

After validating the effectiveness of our proposed method, we conduct
experiments on CUB, CARS and SOP to compare our proposed method
with the state-of-the-art defense methods, \ie, EST~\cite{advrank}
and ACT~\cite{robrank}, as shown in \cref{tab:sota}.
%
An ideal defense method should be able to achieve a high ERS and a high R@1
at a low training cost (\ie, $\eta+1$).
%
The ability of a method to achieve a high ERS under a fixed training cost
indicates a high efficiency.

According to the results, EST[$\mathcal{R}$] achieves a relatively high R@1
when $\eta{=}8$, but suffers from a drastic drop in R@1 when $\eta$ is
increased to $32$.
%
Nevertheless, EST[$\mathcal{R}$] only lead to a moderate robustness in all
settings compared to other methods.
%
Experiments for EST[$\mathcal{S}$] is omitted as it is expected to result in
even much lower ERS based on the observations in previous subsections, and EST
has been greatly outperformed by ACT~\cite{robrank}.
%
Although ACT[$\mathcal{R}$] achieves a relatively high ERS, its R@1 performance
drop is distinct on every dataset.
%
According the previous subsections, ACT[$\mathcal{S}$] can lead to a high R@1,
but along with a significantly lower ERS.
%
Thus, results for ACT[$\mathcal{S}$] are omitted from the table.

Apart from that, our method HM[$\mathcal{S},g_\mathsf{LGA}$] out performs the
previous methods in every aspect, as shown in \cref{fig:introplot} for 
example.
%
Although HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach
a higher ERS, they are excluded from comparison because they induce a
significant performance drop in R@1.

It \emph{must} be acknowledged that the high R@1 performance of our method
largely stems from the source triplet sampling strategy, namely Softhard,
instead of our contribution.
%
In terms of the overall performance, our method can achieve the highest ERS at
the lowest performance drop in R@1 under a fixed training cost.
%
The existing methods are overwhelmingly outperformed by our method.

@@

For adversarial training of a DML model, being selective to both benign and
adversarial training samples is crucial for preventing model collapse, and
achieving good performance on both types of samples.
%
Hardness Manipulation is a flexible tool for us to specify such ``selection'',
and Graduate Adversary is a selection rule for adversarial examples.
%
Intra-Class Structure loss helps the model exploit more information from the
given adversarial examples.

@@

Adversarial robustness is crucial for DML applications.
%
In this paper, we improve adversarial training efficiency through HM.
%
Since regular training and the min-max adversarial training can be expressed as
two boundary cases of HM, Graduate Adversary has been demonstrated effective as
an ``intermediate point'' between the two cases.
%
Enforcing the previously neglected Intra-Class Structure can further improve
model robustness and adversarial training efficiency.
%
Our method outperforms previous methods.

>>>>

After validating the effectiveness of our proposed method, we conduct
experiments on CUB, CARS and SOP to compare our proposed method
with the state-of-the-art defense methods, \ie, EST~\cite{advrank}
and ACT~\cite{robrank}, as shown in \cref{tab:sota}.
%
An ideal defense method should be able to achieve a high ERS and a high R@1
at a low training cost (\ie, $\eta+1$).
%
The ability of a method to achieve a high ERS under a low training cost
indicates a high efficiency.

According to the results, EST[$\mathcal{R}$] achieves a relatively high R@1
when $\eta{=}8$, but suffers from a drastic drop in R@1 when $\eta$ is
increased to $32$.
%
Nevertheless, EST[$\mathcal{R}$] only lead to a moderate robustness
compared to other methods.
%
Experiments for EST[$\mathcal{S}$] are omitted as they are expected to result in
even much lower ERS based on the observations in previous subsections, and EST
has been greatly outperformed by ACT~\cite{robrank}.
%
Although ACT[$\mathcal{R}$] achieves a relatively high ERS, its R@1 performance
drop is distinct on every dataset.
%
According the previous subsections, ACT[$\mathcal{S}$] can lead to a high R@1,
but along with a significantly lower ERS.
%
Thus, results for ACT[$\mathcal{S}$] are omitted for being insufficiently robust.

Apart from that, our method HM[$\mathcal{S},g_\mathsf{LGA}$] outperforms the
previous methods in every aspect, as shown in \cref{fig:introplot} for 
example.
%
Although HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach
a higher ERS, they are excluded from comparison because they induce a
significant performance drop in R@1.

It \emph{must} be acknowledged that the high R@1 performance of our method
largely stems from the source triplet sampling strategy, namely Softhard,
instead of our contribution.
%
In terms of the overall performance, our method can achieve the highest ERS at
the lowest performance drop in R@1 under a fixed training cost.
%
The existing methods are overwhelmingly outperformed by our method in overall
performance.

@@

For adversarial training of a DML model, selectiveness on both benign and
adversarial training samples is crucial for preventing model collapse, and
achieving good performance on both types of samples.
%
HM is a flexible tool for specifying such a ``selection'',
while LGA is a selection rule for adversarial examples.
%
ICS loss term helps the model exploit more information from the
given sextuplet.

The use of existing assets, limitations and societal impact of our method
are discussed in supplementary material.

@@

Adversarial robustness is crucial for DML applications.
%
In this paper, we improve adversarial training efficiency through HM.
%
Since regular training and the min-max adversarial training can be expressed as
two boundary cases of HM, Graduate Adversary has been demonstrated effective as
an ``intermediate point'' between the two cases.
%
Enforcing the previously neglected Intra-Class Structure can further improve
model robustness and adversarial training efficiency.
%
%Our method outperforms previous methods.
